MG7: Configurable and scalable 16S data analysis

### 2016-07-26 docs/mg7-paper/out/paper.tex
add the definition of close, a note for a figure

In any other case, under our assumptions, this assignment should be
discarded.

All these steps are automated, and integrated with every release of our
reference database. The whole process can be repeated and adapted to
other subsets of RNACentral; we do this for a 18S reference database.

>>>>

In any other case, under our assumptions, this assignment should be
discarded. What we consider as close is: the parent of the MG7
assignment should be contained in the lineage of the original
assignment.

All these steps are automated, and integrated with every release of our
reference database. The whole process can be repeated and adapted to
other subsets of RNACentral; we do this for an 18S reference database.
